---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countmaskr

## Development Status

**Alpha Version**: Please be aware that this version is under active development, and some features may be incomplete or subject to change.

<!-- badges: start -->
<!-- badges: end -->

## Overview

The goal of countmaskr is to automate small cell suppression in tabular reports to reduce privacy risk.

### Definitions of small and secondary cells in one dimensional frequency table

### Original 

|Age | N |
| :-- | :- |
| 0 - 1 | <span style="color:red"> **4** </span> |
| 2 - 9 |<span style="color:purple"> **71** </span> |
|10 - 19| 925|
|20 - 29| 0|
|30 - 39| 0|

&nbsp;

-   <span style="color:red"> **small cell** </span> : A cell with a value below defined threshold which requires a suppression. Aka, a primary cell
-   <span style="color:purple"> **secondary cell** </span> : A cell within the contingency table that would suppression to prevent reverse engineering of small(primary) cell through arithmetic operations

&nbsp;

### Solution

|Age | N |
| :-- | :- |
| 0 - 1 | <span style="color:red"> **<11** </span> |
| 2 - 9 |<span style="color:purple"> **<80** </span> |
|10 - 19| 925|
|20 - 29| 0|
|30 - 39| 0|

&nbsp;


## Installation

You can install the **alpha** version of countmaskr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("PEDSnet/countmaskr")
```

&nbsp;

## Getting started
Data: mtcars


```{r example, message=FALSE}
require(countmaskr)
require(tidyverse)
require(knitr)
```

&nbsp;

## One dimensional frequency table

```{r message=F}
data(mtcars)

mtcars %>% count(gear) %>%
  kable()
```

```{r,message=F}
mtcars %>% count(gear) %>%
  mutate(n = mask_counts(n)) %>%
  kable()
```


## Two-by-two frequency table

### Example 1

```{r,message=F}
data(melanoma,package = "boot")

melanoma_fctr <- melanoma %>%
  mutate(
    status = factor(status, levels = c(2, 1, 3), labels = c("Alive", "Melanoma death", "Non-melanoma death")),
    sex = factor(sex, levels = c(1, 0), labels = c("Male", "Female")),
    ulcer = factor(ulcer, levels = c(0, 1), labels = c("Absent", "Present"))
  ) 
```

#### Original 

```{r,message=F}
melanoma_fctr %>% count(status,ulcer) %>%
  pivot_wider(id_cols = 'status',
              names_from = 'ulcer',
              values_from = n) %>%
  kable()
```

#### Masked

```{r,message=F}
melanoma_fctr %>% count(status,ulcer) %>%
  pivot_wider(id_cols = 'status',
              names_from = 'ulcer',
              values_from = n) %>%
  mask_table(col_groups = c("Absent","Present")) %>%
  kable()
```






### Example 2
```{r message=F}
 df <- tibble::tribble(
   ~block, ~Characteristics, ~group1, ~group2, ~group3, ~group4,
   "sex", "Male", 190, 1407, 8, 2,
   "sex", "Female", 17, 20, 511, 2,
   "sex", "Sex - Other", 15, 7, 6, 4,
   "race", "White", 102, 1385, 75, 1,
   "race", "African American / Black", 75, 30, 325, 0,
   "race", "Asian", 20, 9, 100, 2,
   "race", "Native American / Pacific Islander", 15, 10, 4, 3,
   "race", "Race - Other", 10, 0, 21, 2,
 ) %>%
   mutate(
     aggr_group_all = group1 + group2 + group3 + group4,
     aggr_group_1_2 = group1 + group2,
     aggr_group_3_4 = group3 + group4
   ) 
```

#### Orignial 
```{r message=F}
df %>% kable()
```


#### Masked with additional new columns and percentage columns
```{r,message=F}
 mask_table(df,
   group_by = "block",
   col_groups = list(
     c("aggr_group_1_2", "group1", "group2"),
     c("aggr_group_3_4", "group3", "group4")
   ),
   overwrite_columns = F,
   percentages = T
 ) %>%
  kable()
```

# {placeholder for grant related information}

This package was developed to support activities of the PCORnet Query Fulfillment team as well as to support research conducted within PEDSnet, A Pediatric Clinical Research Network. PCORnet Query Fulfillment is funded through Patient-Centered Outcomes Research Institute (PCORI) award RI-CHOP-01-PS2. PEDSnet has been developed with funding from the PCORI; PEDSnet’s participation in PCORnet is funded through PCORI award RI-CHOP-01-PS1. 
 
The package and its documentation do not necessarily represent PCORI or other organizations participating in, collaborating with, or funding PCORnet.
